---
title: "MY472 Final"
output: html_document
date: "2023-12-24"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

OVERALL NOTES:
- You're waiting to hear back on the forum about use of regression techniques
  This is relatively important as you need to compare groups within the same policing area as the rate of stop and search by     area is a primary confounder
- Remember to add readme to github repo - it will be marked too


Chosen Option 1: Number 3 - Police Stop and Search

Research Question:
“In the United Kingdom, a police officer has powers to stop and search any individual if the officer has ‘reasonable grounds’ to suspect the individual is carrying certain items or, under some other conditions, if a senior police officer has granted approval (see here for details). Are there biases in who experiences stop and search by the police?”

## Section 1 - Introduction)

Are there biases in who experiences stop and search by the police?

What is bias in this context?

- Bias is defined as a prejudice against individuals or groups that is considered to be unfair. It may manifest in the disproportionate targeting of certain individuals based on race, ethnicity, age, gender, socioeconomic status or other personal factors, rather than objective evidence or intelligence-based policing. (GPT WROTE THIS)

What are 'reasonable grounds' for stop and search? How can we measure their occurrence relative to any affect of bias?


What are the key statistical aspects of bias?

1) Disproportionality - Are certain groups searched at rates disproportionate to their representation in the population OR to the crime rates associated with that group?
- If we control for crime rates, are certain groups still searched at disproportionate rates?

2) Outcome Discrepancy - Are certain groups more likely to be arrested or charged after being searched?

3) Source of discrimination - do biases originate at the individual level or at the institutional level (senior police officers)?


Where would bias originate?

Police officer - Individual level

Police force - Senior police officer level (Institutional)


What are important factors to account for?

- Are biases genuinely prejudicial in nature, or do they reflect a higher rate of crime in certain areas?

Section 2 - Data)

-Use the 'ukpolice' R package to get the data

```{r}
library(ukpolice)
library(tidyverse)


tv_ss <- ukc_stop_search_force("thames-valley", date = "2018-12")

tv_ss2 <- tv_ss %>% 
  filter(!is.na(officer_defined_ethnicity) & outcome != "" ) %>%
  group_by(officer_defined_ethnicity, outcome) %>%
  summarise(n = n()) %>%
  mutate(perc = n/sum(n))

p1 <- ggplot(tv_ss2, aes(x = outcome, y = perc,
                             group = outcome, fill = outcome)) + 
  geom_col(position = "dodge") + 
  scale_y_continuous(labels = scales::percent,
                     breaks = seq(0.25, 0.8, by = 0.25)) + 
  scale_x_discrete(labels = scales::wrap_format(15)) + 
  theme(legend.position = "none", axis.text.x = element_text(size = 7)) + 
  labs(x = "Outcome", 
       y = "Percentage of stop and searches resulting in outcome",
       title = "Stop and Search Outcomes by Police-Reported Ethnicity",
       subtitle = "Thames Valley Police Department, December 2018",
       caption = "(c) Evan Odell | 2019 | CC-BY-SA") + 
  facet_wrap(~officer_defined_ethnicity)

p1


#List of police forces
police_forces <- ukc_forces()

head(police_forces, 50)

# Retrieve stop and search data for a specific police force for January 2021
crime_data <- ukc_stop_search_force("metropolitan", date = "2023-9")

dim(crime_data)


```




Section 3 - Analysis)



Important Notes:
- Northern Ireland Police Service does not provide stop and search data

Questions:
- Do I cite the things that I need to cite


Section 4 - Code Appendix




