---
title: "MY472_Final"
author: "CT-Dev1"
date: "01/01/2024"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load_packages, eval = TRUE}
#Load required packages
library(ukpolice)
library(tidyverse)
library(sf)
library(sp)
library(httr)
library(jsonlite)
library(RSQLite)
library(httr)
library(netstat)
library(texreg)
library(gtsummary)
```

```{r load_data, eval = TRUE}
#Ethnicity Population Data by LSOAs (downloaded from office for national statistics - 2021 data)
ethnicity_data <- read.csv("data\\LSOA_ethnicity.csv")

#Local District Shape Files from GeoJSON
LSOA_shapes <- st_read("data\\LSOA_shapefiles.geojson")

#Police Force Shape files from GeoJSON
pf_shapes <- st_read("data\\force_areas_shapefiles.geojson")
```

```{r clean_data, eval = TRUE}
#Create table for LSOAs by police force area
LSOA_by_force <- LSOA_shapes %>% 
  st_centroid() %>% 
  st_join(pf_shapes, join = st_intersects) %>% 
  as_tibble() %>%
  select(c(LSOA21CD, LSOA21NM, pfa16cd, pfa16nm)) %>% 
  rename(LSOA_code = LSOA21CD, LSOA_name = LSOA21NM, force_code = pfa16cd, force_name = pfa16nm)

#Create table for population by ethnicity for LSOA
ethnicity_by_LSOA <- ethnicity_data %>% 
  rename(LSOA_code = Lower.layer.Super.Output.Areas.Code, LSOA_name = Lower.layer.Super.Output.Areas, ethnic_group = Ethnic.group..20.categories.) %>%
  select(LSOA_code, Observation, ethnic_group) %>%
  pivot_wider(names_from = ethnic_group, values_from = Observation) %>% 
  mutate(total_pop = rowSums(across(where(is.numeric))))

#Joining the two tables
ethnicity_by_force <- LSOA_by_force %>% 
  full_join(ethnicity_by_LSOA, by = "LSOA_code") %>% 
  group_by(force_code, force_name) %>%
  mutate(force_name = str_replace_all(force_name, " Police", "")) %>%
  summarize(across(where(is.numeric), sum, na.rm = TRUE))

```

```{r get_ss_data, eval = TRUE}
#Create table that relates API input, force name and force code in standard format
police_forces <- ukc_forces()%>% 
  rename(force_name = name, ukc_input = id)%>% 
  mutate(force_name = str_replace_all(force_name, " Police", "")) %>% 
  mutate(force_name = str_replace_all(force_name, " Constabulary", "")) %>% 
  mutate(force_name = str_replace_all(force_name, "&", "and")) %>%
  mutate(force_name = str_replace_all(force_name, " Service", "")) %>%
  inner_join(ethnicity_by_force, by = "force_name") %>% 
  select(force_name, ukc_input, force_code)

#Vector of months to loop through, input into API
dates <- c("2022-01","2022-02","2022-03","2022-04","2022-05","2022-06","2022-07","2022-08","2022-09","2022-10","2022-11","2022-12")
```


```{r get_ss_data_2, eval = FALSE}
#Function to clean the raw data from API
clean_ss_data <- function(ss_data, force, month) {
  force_data <- ss_data %>% 
    mutate(ukc_input = force) %>% 
    inner_join(police_forces, by = "ukc_input") %>% 
    select(age_range, gender, self_defined_ethnicity, officer_defined_ethnicity, legislation, object_of_search, outcome_object_name, legislation, force_code, force_name, ukc_input) %>% 
    mutate(self_defined_ethnicity = ifelse(grepl("Not stated", self_defined_ethnicity), NA, self_defined_ethnicity)) %>% 
    mutate(racial_group = ifelse(is.na(self_defined_ethnicity), officer_defined_ethnicity, self_defined_ethnicity)) %>% 
    #Add column for racial_group based on ethnicity classification
    mutate(racial_group = ifelse(grepl("White", racial_group, fixed = TRUE), 'White',
                           ifelse(grepl("Asian", racial_group, fixed = TRUE), 'Asian',
                           ifelse(grepl("Black", racial_group, fixed = TRUE), 'Black',
                           ifelse(grepl("Mixed", racial_group, fixed = TRUE), 'Mixed',
                           ifelse(grepl("Other", racial_group, fixed = TRUE), 'Other', NA)))))) %>% 
    mutate(month = month)
  return(force_data)
}

#Script to download stop and search data for all police forces over 2022
'
#Empty tibble to store the data
stop_search_2022 <- ukc_stop_search_force("bedfordshire","2022-01") %>%
  clean_ss_data("bedfordshire", "2022-01") %>%
  slice(0)

#table to store missing forces and months
missing_data = tibble(ukc_input = character(), month = character())

#Loop over all police forces and months
for (month in dates){
  for (force in police_forces$ukc_input){
    force_data <- ukc_stop_search_force(force, month)
    if (length(force_data)==0 | is.null(force_data)){
      missing_data <- missing_data %>% 
        add_row(ukc_input = force, month = month)
      next
    } else {
    stop_search_2022 <- force_data %>% 
      clean_ss_data(force, month) %>%
      rbind(stop_search_2022)
    }}
  Sys.sleep(3) 
}
'
```


```{r partial_missing_data_fill, eval = FALSE}
#There is missing data, so investigate police API issue log at https://data.police.uk/changelog/
#Some forces have partial missing data for 2022, so we will utilize forward propagation to fill in the data
'
#Create table of partial missing data
partial_missing_forces <- missing_data %>% 
  filter(ukc_input %in% c("greater-manchester","gwent", "north-yorkshire")==FALSE) %>% 
  mutate(month_index = as.numeric(str_replace_all(month, "2022-", ""))) 

#create table of inputs for forward propagation
forward_prop_input <- missing_data %>% 
  filter(ukc_input %in% c("greater-manchester","gwent", "north-yorkshire")==FALSE) %>% 
  group_by(ukc_input) %>%
  summarize(missing_months = n()) %>% 
  inner_join(police_forces, by = "ukc_input")

#Script to loop over missing data by force and month

for (force in forward_prop_input$ukc_input){
  missing_months <- forward_prop_input$missing_months[forward_prop_input$ukc_input==force]
  last_record_month <- min(partial_missing_forces$month_index[partial_missing_forces$ukc_input==force]) -1
  month_input <- paste0("2022-", last_record_month)
  for (i in 1:forward_prop_input$missing_months[forward_prop_input$ukc_input==force]){
    force_data <- ukc_stop_search_force(force, month_input)
    month_filled_input <- paste0("2022-", last_record_month+i)
    stop_search_2022 <- force_data %>% 
      clean_ss_data(force, month_filled_input) %>%
      rbind(stop_search_2022)
  }
}

#Write to disk, this is commented out, data is stored in stop_search_2022.csv in data folder (within the github)
write_csv(stop_search_2022, "stop_search_2022.csv")
'
```


```{r load_ss_data, eval = TRUE}
#Load full dataset from csv, which is only missing data for Greater Manchester, Gwent and North Yorkshire, these I add manually at later stages
stop_search_2022 <- read_csv("data//stop_search_2022.csv")
```

```{r missing_data_test, eval = FALSE}
#test that forward propagation worked using the test case of South Wales, which previously had some missing data
'
stop_search_2022 %>% 
  filter(force_name == "South Wales") %>% 
  group_by(month) %>% 
  summarize(total_stops = n()) %>% 
  print()

#Demonstration that API fails for some forces - greater manchester, gwent and north yorkshire
url <- "https://data.police.uk/api/stops-force?force=greater-manchester&date=2022-02"
json <- content(GET(url), "parsed")
print(is.null(json)|length(json)==0)
'
```

```{r total_missing_data_fill, eval = TRUE}
#North Yorkshire, Gwent and Greater Manchester have no ethnicity data at all for any period
#Given this, can extract from alternative data source, Home office stop and search by ethnicity of 2022

#download this missing data from gov.uk - this was done previously, data stored in missing_forces_stop_search.csv

#url <- "https://www.ethnicity-facts-figures.service.gov.uk/crime-justice-and-the-law/policing/stop-and-search/latest/downloads/stop-and-search-#data-2006-2022.csv"
#download.file(url, destfile = "missing_forces_stop_search.csv")
missing_forces_ss <- read.csv("data/missing_forces_stop_search.csv")

#Process the data to filter for the missing police forces, keep it for later use to input missing data
#Full data set
missing_forces_to_input <- missing_forces_ss %>% 
  rename(number_of_stop_and_searches_ethnicity_reported = total_number_of_stop_and_search_carried_out_in_this_year_in_this_area_excluding_cases_where_the_ethnicity_was_unreported, stop_search_rate_ethnicity = proportion_of_total_stop_and_searches_of_this_ethnicity_in_the_financial_year_excludes_unreported) %>%
  mutate(time = as.character(time)) %>% 
  filter(geography %in% c("Gwent", "Greater Manchester", "North Yorkshire")==TRUE) %>% 
  filter(geography_type == "Police Force Area" & time == "2021/22") %>% 
  select(ethnicity, geography, number_of_stop_and_searches, number_of_stop_and_searches_ethnicity_reported, population_by_ethnicity, rate_per_1_000_population_by_ethnicity, stop_search_rate_ethnicity)

#Total rate by force (for Gwent, Manchester, N Yorkshire)
missing_forces_ss_rate <- missing_forces_to_input %>% 
  select(ethnicity, geography, population_by_ethnicity, number_of_stop_and_searches)
```

```{r ss_by_race_tables, eval = TRUE}
#race populations by force area
race_by_force <- ethnicity_by_force %>% 
  pivot_longer(cols = -c(force_code,force_name), names_to = "racial_group", values_to = "population") %>% 
  mutate(racial_group = ifelse(grepl("White", racial_group, fixed = TRUE), 'White',
                       ifelse(grepl("Asian", racial_group, fixed = TRUE), 'Asian',
                       ifelse(grepl("Black", racial_group, fixed = TRUE), 'Black',
                       ifelse(grepl("Mixed", racial_group, fixed = TRUE), 'Mixed',
                       ifelse(grepl("Other", racial_group, fixed = TRUE), 'Other', NA)))))) %>%
  group_by(force_name, racial_group) %>% 
  summarize(population = sum(population[racial_group==racial_group])) %>% 
  filter(is.na(racial_group)==FALSE) %>%
  pivot_wider(names_from = racial_group, values_from = "population", names_prefix = "population_") %>% 
  mutate(population_Total = population_White + population_Black + population_Mixed + population_Asian + population_Other) %>%
  inner_join(police_forces, by = "force_name")

#rate of stop and search by race
race_stops_data <- stop_search_2022 %>% 
  mutate(self_defined_ethnicity = ifelse(grepl("Not stated", self_defined_ethnicity), NA, self_defined_ethnicity)) %>% 
  filter(is.na(self_defined_ethnicity)==FALSE) %>%
  group_by(force_name) %>% 
  summarize(total_stops_ethnicity_reported = n(), black_stops = sum(racial_group=="Black"), white_stops = sum(racial_group=="White"), mixed_stops = sum(racial_group=="Mixed"), asian_stops = sum(racial_group=="Asian"), other_stops = sum(racial_group=="Other")) %>%  
  inner_join(police_forces, by = "force_name") %>%
  inner_join(race_by_force, by = c("force_name","force_code")) %>% 
  mutate(stop_rate_black = (black_stops/population_Black)*1000, stop_rate_white = (white_stops/population_White)*1000, stop_rate_mixed = (mixed_stops/population_Mixed)*1000, stop_rate_asian = (asian_stops/population_Asian)*1000, stop_rate_other = (other_stops/population_Other)*1000, stop_rate_total = (total_stops_ethnicity_reported/population_Total)*1000)
```
- add number of stop and searches no ethnicity reported
-note that the rate is based on the number of stops where ethnicity is reported, this can change the rate significantly
- in the above, the total stop and searches are those with no ethnicity reported

```{r visualize_total_ss_rate, eval=TRUE}
#Visualizing search rate by police force area

#total stops by force for N yorkshire, Gwent and Greater Manchester (The missing data)
total_stops_man_gwent_yorkshire <- missing_forces_to_input %>% 
  select(geography, number_of_stop_and_searches, ethnicity) %>%
  group_by(geography) %>%
  summarize(total_stops = sum(number_of_stop_and_searches[ethnicity == ethnicity])) %>% 
  rename(force_name = geography)

#Total stops by force (complete data)
ss_rate_by_force <- stop_search_2022 %>% 
  group_by(force_name) %>%
  summarize(total_stops = n()) %>% 
  rbind(total_stops_man_gwent_yorkshire) %>% 
  inner_join(race_by_force, by = c("force_name")) %>%
  mutate(stop_rate_total = (total_stops/population_Total)*1000) %>%
  select(force_name, stop_rate_total) %>% 
  #Exclude City of London, as it is an outlier, it skews the graph range, mkaing variability invisible
  filter(force_name != "City of London")

#Generating the visualization data, combining with the force shapefile dataframe
map_data <- pf_shapes %>% 
  rename(force_name = pfa16nm) %>% 
  mutate(force_name = ifelse(force_name=="Metropolitan Police", "Metropolitan", force_name)) %>%
  filter(force_name != "City of London") %>%
  inner_join(ss_rate_by_force, by = "force_name")

#creating visualization map of England and Wales
map1 <- ggplot(map_data, aes(fill = stop_rate_total)) +
  geom_sf() +
  scale_fill_viridis_c(option = "plasma", direction = -1, na.value = "grey90", name = "Stop and search rate per 1000 people") +
  theme_void() +
  theme(legend.position = "bottom") +
  labs(title = "Stop and Search Rate by Police Force Area", subtitle = "2021/22", caption = "Source: Police.uk, 2022, based on number of searches that recorded racial/ethnicity data")

map1  #display the map
```

Notes on above:
- We exclude the City of London due to the number of people who visit compared to the small number of people who live there


Now, to run some statistical tests using linear regression
```{r regression_full_data, eval=TRUE}
#Table of stops by race by force, tidy long format
race_stops_data_long <- race_stops_data %>% 
  select(stop_rate_black, stop_rate_white, stop_rate_mixed, stop_rate_asian, stop_rate_other, force_name) %>%
  rename(Black = stop_rate_black, White = stop_rate_white, Mixed = stop_rate_mixed, Asian = stop_rate_asian, Other = stop_rate_other) %>%
  pivot_longer(cols = c(Black, White, Mixed, Asian, Other), names_to = "racial_group", values_to = "stops_rate_per_1000") %>% print()

#Data for regression - total population = the 
regression_data <- stop_search_2022 %>% 
  mutate(self_defined_ethnicity = ifelse(grepl("Not stated", self_defined_ethnicity), NA, self_defined_ethnicity)) %>% 
  filter(is.na(self_defined_ethnicity)==FALSE) %>%
  inner_join(race_stops_data_long, by = c("racial_group","force_name")) %>% 
  filter(force_name != "City of London") %>%
  mutate(racial_group = as_factor(racial_group), force_name = as_factor(force_name)) %>% 
  rename(Male = gender) %>% 
  mutate(Male = ifelse(Male == "Male", 1, 0)) 

#Multiple Linear Regression model, finding effect of race, force area, male gender on likelihood of being stopped 
#set the reference groups to be white for racial group and Kent for force area, as it has near-average stop and search rate (6.78 per 1000)
reg1 <- lm(stops_rate_per_1000 ~ relevel(racial_group, ref="White") + relevel(force_name, ref="Kent") + Male, data = regression_data)

#Tidy Present
tbl_regression(reg1)
```




```{r}
#Number of searches by ethnicity by force
ethnicity_stops <- stop_search_2022 %>% 
    mutate(self_defined_ethnicity = ifelse(grepl("Not stated", self_defined_ethnicity), NA, self_defined_ethnicity)) %>% 
    filter(is.na(self_defined_ethnicity)==FALSE) %>% 
    group_by(self_defined_ethnicity, force_name) %>% 
    summarize(total_stops = n()) %>% 
    pivot_wider(names_from = self_defined_ethnicity, values_from = total_stops)


harmonize_ethnicity <- function(ethnicity) {
  # Define the mapping between census and police ethnicities
  mapping <- list(
    "Asian, Asian British or Asian Welsh: Other Asian" = "Asian/Asian British - Any other Asian background",
    "White: English, Welsh, Scottish, Northern Irish or British" = "White - English/Welsh/Scottish/Northern Irish/British",
    "Does not apply" = NA,
    "Mixed or Multiple ethnic groups: Other Mixed or Multiple ethnic groups" = "Mixed/Multiple ethnic groups - Any other Mixed/Multiple ethnic background",
    "White: Other White" = "White - Any other White background",
    "Black, Black British, Black Welsh, Caribbean or African: African" = "Black/African/Caribbean/Black British - African",
    "Black, Black British, Black Welsh, Caribbean or African: Other Black" = "Black/African/Caribbean/Black British - Any other Black/African/Caribbean background",
    "Asian, Asian British or Asian Welsh: Pakistani" = "Asian/Asian British - Pakistani",
    "Asian, Asian British or Asian Welsh: Bangladeshi" = "Asian/Asian British - Bangladeshi",
    "Other ethnic group: Any other ethnic group" = "Other ethnic group - Any other ethnic group",
    "Mixed or Multiple ethnic groups: White and Black African" = "Mixed/Multiple ethnic groups - White and Black African",
    "White: Gypsy or Irish Traveller" = "White - Gypsy or Irish Traveller",
    "Mixed or Multiple ethnic groups: White and Black Caribbean" = "Mixed/Multiple ethnic groups - White and Black Caribbean",
    "Other ethnic group: Arab" = "Other ethnic group - Arab",
    "White: Irish" = "White - Irish",
    "Black, Black British, Black Welsh, Caribbean or African: Caribbean" = "Black/African/Caribbean/Black British - Caribbean",
    "Mixed or Multiple ethnic groups: White and Asian" = "Mixed/Multiple ethnic groups - White and Asian",
    "Asian, Asian British or Asian Welsh: Indian" = "Asian/Asian British - Indian",
    "Asian, Asian British or Asian Welsh: Chinese" = "Asian/Asian British - Chinese"
  )
  # Return the corresponding police ethnicity, or NA if no match is found
  return(ifelse(ethnicity %in% names(mapping), mapping[[ethnicity]], NA))
}

ethnicity_by_force_harmonized <- ethnicity_by_force %>% 
  pivot_longer(names_to = "ethnicity", values_to = "total_stops",cols= -c(force_code,force_name))

#ENCOUNTERS ERROR WITH THE ABOVE


#rate per 1000 population by ethnicity by force
ethnicity_stop_rates <- ethnicity_stops %>% 
  

inner_join(ethnicity_by_force, by = "force_name") %>%
  print()
  
```


```{r}
#number of searches by ethnicity
  ss_analysis_ethnicity <- force_data %>% 
    select(age_range, gender, self_defined_ethnicity, officer_defined_ethnicity, legislation, object_of_search, outcome_object_name, legislation) %>%
    mutate(self_defined_ethnicity = ifelse(grepl("Not stated", self_defined_ethnicity), NA, self_defined_ethnicity)) %>% 
    filter(is.na(self_defined_ethnicity)==FALSE) %>% 
    group_by(self_defined_ethnicity) %>% 
    summarize(total_stops = n(), male_stops = sum(grepl("Male",gender)), female_stops = sum(grepl("Female",gender)))
  
  #full population analysis
  ss_analysis_total_pop <- force_data %>% 
    select(age_range, gender, self_defined_ethnicity, officer_defined_ethnicity, legislation, object_of_search, outcome_object_name, legislation) %>%
    summarize(total_stops = n(), male_stops = sum(grepl("Male",gender)), female_stops = sum(grepl("Female",gender)))
  
  #join into larger table
  ss_data <- ethnicity_by_force %>% 
    full_join()
  
}
  

```


To think about:
- Writing to database
- Get database on all stop and search data for time period for each police force 
- Then you can query it to get all the relevant statistics
- Instead of using crime statistics to determine if there is bias, you can look at the rate of arrest by stop and search


Notes on above:
- You'll have to replace the path with a path online - replicable - however all the data sources are the best available
- Remember to change the above ethnicity_data path to an original data source - its currently on the data you've pre-edited
- add in age data later on


Notes on above:
- If you have time, rename all the variables to be consistent across all dataframes
- Reference the fact that you tested the level of distortion so that it is not too extreme
- If you have time, put all the data frames into a SQL database and query it for analyses where local district code is the primary key



```{r}

#find all the different ethnicity types in the stop search data
metro_force_data <- ukc_stop_search_force("metropolitan", "2021-06")
ethnicity_bins <- unique(metro_force_data$self_defined_ethnicity)
ethnicity_bins[is.na(ethnicity_bins)] <- "NA" #string representation of NA

#Creating a dictionary of ethnicity types
#Represents the 18 ethnicity bins used in the stop_search data
ethnicity_dict <- c("NA" = "NA", "Other ethnic group - Not stated" = "NA", 
                    "Black/African/Caribbean/Black British - African" = "black_african", 
                    "Asian/Asian British - Pakistani" = "asian_pakistani", 
                    "White - Any other White background" = "white_other", 
                    "Asian/Asian British - Any other Asian background" = "asian_other", 
                    "White - English/Welsh/Scottish/Northern Irish/British" = "white_british", 
                    "Black/African/Caribbean/Black British - Any other Black/African/Caribbean background" = "black_other", 
                    "Mixed/Multiple ethnic groups - White and Black Caribbean" = "mixed_white_black_caribbean", 
                    "Other ethnic group - Any other ethnic group" = "other", 
                    "Asian/Asian British - Indian" = "asian_indian", 
                    "Mixed/Multiple ethnic groups - Any other Mixed/Multiple ethnic background" = "mixed_other", 
                    "Black/African/Caribbean/Black British - Caribbean" = "black_carribean", 
                    "Asian/Asian British - Chinese" = "asian_chinese", 
                    "White - Irish" = "white_irish", 
                    "Mixed/Multiple ethnic groups - White and Black African" = "mixed_white_black_african", 
                    "Mixed/Multiple ethnic groups - White and Asian" = "mixed_white_asian", 
                    "Asian/Asian British - Bangladeshi" = "asian_bangladeshi")

#Constructing the data frames to store results by district
NA_data_by_district_ethnicity <- as.tibble(data.frame(district_code = local_districts$LAD22CD, district_name = local_districts$LAD22NM))
ss_by_district_race <- as.tibble(data.frame(district_code = local_districts$LAD22CD, district_name = local_districts$LAD22NM, total_stops = NA, white_stops = NA, asian_stops = NA, black_stops = NA, mixed_stops = NA, other_stops = NA))
#ethnicity data by district
ss_by_district_ethnicity <- as.tibble(data.frame(district_code = local_districts$LAD22CD, district_name = local_districts$LAD22NM))
na_matrix <- matrix(NA, ncol = length(ethnicity_bins), nrow = 331)
colnames(na_matrix) <- ethnicity_bins
ss_by_district_ethnicity <- cbind(ss_by_district_ethnicity, na_matrix)
                                      
#BUILDING FUNCTION TO AGGREGATE THE DATA by LOCAL DISTRICT - STARTING WITH STOP-SEARCH RATES
district_data <- ukc_stop_search_poly(local_districts[309,], "2021-06")

#error handling
if (is.null(district_data)) {
  print("here")
} else {
    print("there")
  }

#
NA_responses <- district_data %>%
  #replace self defined ethnicity which is 'ethnicity not stated' as NA
  mutate(self_defined_ethnicity = ifelse(grepl("Not stated", self_defined_ethnicity, fixed = TRUE), NA, self_defined_ethnicity)) %>% 
  #filter for the rows with no racial/ethnicity data whatsoever
  filter(is.na(self_defined_ethnicity) & is.na(officer_defined_ethnicity)) %>%
  #create new column that defaults to self_defined_ethnicity unless is NA, then officer defined ethnicity
  mutate(race = ifelse(is.na(self_defined_ethnicity), officer_defined_ethnicity, self_defined_ethnicity)) %>%
  summarize(stops_w_missing_ethnicity = sum(is.na(race))) %>% 
  mutate(district_code = local_districts[309,]$LAD22CD, district_name = local_districts[309,]$LAD22NM) %>%  #FORMAT LATER SO IT JUST REFERS TO THE DISTRICT BEING ITERATED OVER
  print()

#Add Na_responses to the NA_data_by_district_ethnicity data frame
full_join(NA_data_by_district_ethnicity, NA_responses, by= "district_code") %>% print()


district_ethnicity_data <- district_data %>% 
  #remove rows with no ethnicity data
  filter(is.na(self_defined_ethnicity)==FALSE | is.na(officer_defined_ethnicity)==FALSE) %>%
  #replace self defined ethnicity which is 'ethnicity not stated' as NA
  mutate(self_defined_ethnicity = ifelse(grepl("Not stated", NA, self_defined_ethnicity))) %>% 
  #create new column that defaults to self_defined_ethnicity unless is NA, then officer defined ethnicity
  mutate(ethnicity = ifelse(is.na(self_defined_ethnicity), officer_defined_ethnicity, self_defined_ethnicity)) %>% 
  #Classify each search as its umbrella ethnicity group (ie. race)
  mutate(umbrella_ethnicity = ifelse(grepl("White", ethnicity, fixed = TRUE), 'White',
                             ifelse(grepl("Asian", ethnicity, fixed = TRUE), 'Asian',
                             ifelse(grepl("Black", ethnicity, fixed = TRUE), 'Black',
                             ifelse(grepl("Mixed", ethnicity, fixed = TRUE), 'Mixed',
                             ifelse(grepl("Other", ethnicity, fixed = TRUE), 'Other', NA)))))) %>% 
  #summarize the data
  #count the number of instances of each ethnic umbrella group
  group_by(umbrella_ethnicity) %>% 
  #sum the number of each ethnicity
  tally() %>% print()
  
  
  
district_ethnicity_data <- district_data %>% 
  filter(is.na(self_defined_ethnicity)==FALSE | is.na(officer_defined_ethnicity)==FALSE) %>%
  #create new column that defaults to self_defined_ethnicity, else officer defined ethnicity
  mutate(ethnicity = ifelse(is.na(self_defined_ethnicity), officer_defined_ethnicity, self_defined_ethnicity)) %>% 
  #Add an ethnic umbrella group indicator
  mutate(umbrella_ethnicity = ifelse(grepl("White", ethnicity, fixed = TRUE), 'White',
                                     ifelse(grepl("Asian", ethnicity, fixed = TRUE), 'Asian',
                                     ifelse(grepl("Black", ethnicity, fixed = TRUE), 'Black',
                                     ifelse(grepl("Mixed", ethnicity, fixed = TRUE), 'Mixed',
                                     ifelse(grepl("Other", ethnicity, fixed = TRUE), 'Other', NA)))))) %>% 
  #summarize the data
  #count the number of instances of each ethnic umbrella group
  group_by(self_defined_ethnicity) %>% 
  #sum the number of each ethnicity
  tally() %>% print()
  




```
Notes on above:
- IF you want to summarize the individual ethnic bins then you can just add more to the mutate ifelse batch
- Note that if there are no ethnicity matches to the categories, it outputs an NA
- you need to add handling for the not-stated category in the data
- What if we include the mixed race people within their most visible racial category? (ie. black, white, asian, other)

Incongruencies (thigns in census data not in stop_search data):
- Gypsy and Irish Traveller is not recorded as an option in the stop search ethnicity data
- White: Roma
- Any other ethnic background: Arab

Things included in stop_search data but not in census data:
- Other ethnic group: Not stated
- NA

Dealing with NA data:
- Clearly state the proportion of stop and search records with missing ethnicity data in each district
- Consider doing a sensitivity analysis - see how different approaches to handling NA data (including vs. excluding) affect your results
- Discuss Potential Implications of NA data, are there any patterns (certain districts, time periods)

Dealing with no location data:
- This obviously makes the use of poly shapes less reliable
- use a robustness check on the rates of stop/search within the ukc_stop_search no location function


```{r}
#NEXT STEPS

# 1) Aggregate the necessary crime, ethnicity data in batches so you never store a full dataframe with all the information that is being analyzed in total

# use the table in the folder on ethnicity statistics by local district area

```


```{r}
#Pass the shs files as arguments to the API

#ukc_stop_search_poly - see usage


```


Now to begin the data analysis

```{r}
#apply sf_simplify and st_transform to all the shape files
local_districts_simp <- st_transform(st_simplify(local_districts, dTolerance = 50), crs = 4326)

#create function that gets the monthly stop_search data for each local district

get_stop_search_by_month <- function(search_month){
  #create empty dataframe
  stop_search_df <- data.frame()
  #loop over all the local districts
  for (i in 1:nrow(local_districts_simp)){
    #pass to the API
    data <- ukc_stop_search_poly(local_districts_simp[i,],search_month)
    #append to the dataframe
    stop_search_df <- rbind(stop_search_df, data)
  }
  return(stop_search_df)
}

for (i in 1:nrow(local_districts_simp)){
  #convert to latlong
  local_districts_simp_latlong <- st_transform(local_districts_simp, crs = 4326)
  #pass to the API
  data <- ukc_stop_search_poly(local_districts_simp_latlong[i,],"2022-01")
  #save the data
  save(data, file = paste0("C:\\Users\\rhrou\\OneDrive\\Desktop\\ASDS\\MY472\\MY472-Final\\usable_data\\",local_districts_simp_latlong$LAD22NM[i],".RData"))
}



```




```{r}
age_gender_data <- read.csv("C:\\Users\\rhrou\\OneDrive\\Desktop\\ASDS\\MY472\\MY472-Final\\usable_data\\local_district_population_age_gender.csv")

age_gender_districts <- unique(age_gender_data$Lower.tier.local.authorities.Code)

ethnicity_data <- read.csv("C:\\Users\\rhrou\\OneDrive\\Desktop\\ASDS\\MY472\\MY472-Final\\usable_data\\ethnicity_data_pop_numbers.csv")

ethnicity_districts <- unique(ethnicity_data$Area.code)

shape_file_districts <- unique(local_districts$LAD22CD)

#find the districts in age_gender_districts not in ethnicity_districts

print(sum(shape_file_districts %in% ethnicity_districts == FALSE))

print(local_districts$LAD22CD[local_districts$LAD22CD %in% age_gender_districts == FALSE])

local_districts$LAD22CD %in% age_gender_districts

print(sum(is.na(age_gender_data$Lower.tier.local.authorities.Code)))


#remove all rows from local_districts which are not in age_gender_districts

local_districts_test <- local_districts[local_districts$LAD22CD %in% unique(age_gender_data$Lower.tier.local.authorities.Code),]





ukc_stop_search_poly(local_districts_simp[286,],"2022-06")


local_districts_simp[2,]$LAD22NM



```



